---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# rkeepass

<!-- badges: start -->
[![R-CMD-check](https://github.com/schochastics/rkeepass/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/schochastics/rkeepass/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

rkeepass reads [KeePass](https://keepass.info/) `.kdbx` database files directly from R.
It supports KDBX versions 3.x and 4.x with automatic format detection. The heavy lifting
is done by the Rust crate [keepass-rs](https://github.com/sseemayer/keepass-rs).

## Installation

You can install the development version of rkeepass from [GitHub](https://github.com/schochastics/rkeepass) with:

``` r
# install.packages("pak")
pak::pak("schochastics/rkeepass")
```

### System requirements

You need a working [Rust](https://www.rust-lang.org/tools/install) toolchain (rustc >= 1.85).

## Example

```{r example}
library(rkeepass)

# read a KeePass database with a master password
db <- kdbx_read(
  system.file("extdata", "example.kdbx", package = "rkeepass"),
  password = "test123"
)

db
```

The result is a data.frame with one row per entry, and the `group_path` column preserves the folder structure of the database.
Passwords are masked when printing, but the `password` column holds the decrypted values:

```{r}
db$password[db$title == "GitHub"]

print(db, reveal = TRUE)
```

```{r}
# filter by group
db[db$group_path == "Root/Internet", ]
```

Key files can be used instead of (or in addition to) a password:

```r
kdbx_read("my_database.kdbx", password = "secret", keyfile = "my.key")
```
